\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\geometry{margin=1in}

\title{FAASI-CORE: A Benchmark Framework for Evaluating Autonomous Agent Reliability in Long-Horizon Tool-Augmented Workflows}
\author{David Carmel Alex \\ Fusion Civilization Research Institute (FCRI)}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Autonomous AI agents increasingly operate across multi-step environments requiring tool use, recovery from failure, memory continuity, ambiguity resolution, and safety-aware execution. Existing benchmarks partially evaluate model capability but insufficiently isolate operational reliability under long-horizon autonomous execution. FAASI-CORE introduces a benchmark framework for autonomous reliability science.
\end{abstract}

\section{Introduction}
As autonomous AI systems evolve from conversational interfaces into persistent operational agents, benchmark methodology must evolve accordingly.

\section{Problem Statement}
Current evaluation ecosystems insufficiently measure recovery resilience, ambiguity governance, memory integrity, execution stability, and long-horizon autonomous reliability.

\section{Related Work}
HELM, SWE-bench, GAIA, and AgentBench provide important prior foundations.

\section{Methodology}
FAASI benchmark dimensions include task success, tool reliability, recovery intelligence, memory integrity, safety compliance, ambiguity governance, stability, and efficiency.

\section{Scoring Formalism}
\[
FAASI = \sum_{i=1}^{n} w_i m_i
\]
where $m_i$ represents benchmark metrics and $w_i$ dimension weights.

\section{Threats to Validity}
Prototype maturity and benchmark scope limitations remain.

\section{Ethics}
Benchmark design should encourage safety-conscious autonomous system evaluation.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
